Viscous Transport in Eroding Porous Media

### 2019-05-08 docs/transport/erosion_transport.tex
doing the transport paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{A single body eroding in Stokes flow. Color indicates the shear stress on the body. In this simulation, we use three minimum body-to-wall initial distances $d=h$(left), $h/2$(middle), and $h/10$(right) with $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt$, and smoothing parameters of $\eps $ and $\sigma $.}
\label{} 
\end{center}
\end{figure}
{\color{red} We first consider a single circular body in a shear flow. The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$. Let the radius of the body be $r$, the length of the body be $L$, $N_\iin$ and $N_\out$ be the number of discretization points on the body and wall respectively, $h=L/N_\iin$ be the resolution mesh size of the body, and $d$ be the minimum initial distance from body to wall. 
To investigate the shape of eroding body when it is close to wall, we set $r=0.4$, $N_\iin=256$, and $N_\out=1024$ with respect to three different $d=h, h/2$, and $ h/10$.

@@

\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense_201}
\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense_301}
\caption{Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition. The color is the vorticity of fluid. The 4 snapshots are evenly spaced in time. In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps $ and $\sigma $.}
\label{} 
\end{center}
\end{figure}
\subsection{20 nearly touching bodies}
{\color{red} 
By using Barycentric quadrature rule, we are able to capture the details in the fluid when wall and bodies or body and bodies are close to each other. The first nearly touching bodies case is 20 bodies in a Hagen-Poiseuille flow. The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=(1+x_2)(1-x_2)$. The number of discretization points $N_\iin$ on the bodies is 256 and the number of discretization points $N_\out$ on the outer boundary is 1024. 
}

@@

\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b210}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b240}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b270}
\caption{The trajectories of tracers in the fluid with 20 bodies. The 9 snapshots are evenly spaced in time.}
\end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{50 nearly touching bodies}
{\color{red}
The second nearly touching bodies case is 50 bodies in a Hagen-Poiseuille flow.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{s:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{A single body eroding in Stokes flow. Color indicates the shear stress on the body. In this simulation, we use three minimum body-to-wall initial distances $d=h$(left), $h/2$(middle), and $h/10$(right) with $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt$, and smoothing parameters of $\eps $ and $\sigma $.}
\label{} 
\end{center}
\end{figure}
{\color{red} We first consider a single circular body in a shear flow. The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$. Let the initial radius of the body be $r$, the initial length of the body be $L$, $N_\iin$ and $N_\out$ be the number of discretization points on the body and wall respectively, $h=L/N_\iin$ be the resolution mesh size of the body, and $d$ be the minimum initial distance from body to wall. 
To investigate the shape of eroding body when it is close to wall, we set $r=0.4$, $N_\iin=256$, and $N_\out=1024$ with respect to three different $d=h, h/2$, and $ h/10$.

@@

\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense_201}
\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense_301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition. The color is the vorticity of fluid. The 4 snapshots are evenly spaced in time. In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.}
\end{center}
\end{figure}
\subsection{20 nearly touching bodies}
{\color{red} 
By using Barycentric quadrature rule, we are able to capture the details in the fluid when wall and bodies or body and bodies are close to each other. The first nearly touching bodies case is 20 bodies in a Hagen-Poiseuille flow. The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=(1+x_2)(1-x_2)$. The number of discretization points $N_\iin$ on the bodies is 256 and the number of discretization points $N_\out$ on the outer boundary is 1024.

The snapshots of the process of 20 nearly touching bodies eroding are in Fig.~\ref{fig:Eroding20vort}. 
We place some bodies to nearly contact not only one another but also the outer boundary. For example, bodies 1, 6, 13, and 15 are very close to outer boundary. In~\cite{qua-moo2018} we reported the quick expanding space at the narrow channel between neighboring bodies, the developing flat faces at the sites of near contact, and bodies vanishing. In this nearly touching bodies structure, we also observe these phenomena but with more new details.
For the speed of expanding space at the narrow channel, we see some narrow channels do expand faster than other wider channels. For example, the spacing between bodies 14 \& 18 is smaller than the spacing between bodies
 7 \& 14 initially and the former one is comparable to the latter one by the second frame. But there are some small initial spacings that do not expand that much at all by the fourth frame, for example between bodies 1 \& 6, 3 \& 9. 
We could find the explanation from the tracer test in Fig.~\ref{fig:Eroding20tracer}. Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally. If the trajectory of tracer }

@@

\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b210}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b240}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b270}
\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in the fluid with 20 bodies. The 9 snapshots are evenly spaced in time. The tracers are evenly spread in the $x_2-$direction and released at $x_1=-1$.}
\end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{50 nearly touching bodies}
{\color{red}
The second nearly touching bodies case is 50 bodies in a Hagen-Poiseuille flow.
}

\subsection{100 bodies}
{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{s:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
